---
title: "miss data highlights"
author: "Ellen Graham"
date: "5/3/2020"
output: html_document
---

```{r}
library(dplyr)
library(tidyr)
library(readr)
library(lubridate)
library(ggplot2)
library(ggridges)
```

```{r}
all_legs <- read_csv("all_legs_non_median.csv")
all_legs_median <- read_csv("all_legs_median.csv")
```

### Total data points
```{r}
dim(all_legs)
head(all_legs)
head(all_legs_median)
dim(all_legs_median)
```

145366 observations, each with 19 variables, 25260 observations after taking median of 15 second chunks


### Average per minute
```{r}
all_legs %>% 
  mutate(num_in_minute = (time_in_sec%/%60)*60) %>% 
  group_by(num_in_minute) %>% 
  count() %>% 
  pull(n)  %>% 
  mean()
```

On average, 22.13 observations are taken every second.

### Biggest Elevation Change in a Day

(using all legs median)
```{r}
all_legs_median %>% 
  mutate(date = as_date(date_time)) %>% 
  ggplot(aes(x = alt, y = as.character(date), height = stat(density))) + 
  geom_density_ridges(stat = "binline", binwidth = 10, scale = 0.95, draw_baseline = FALSE)
 
all_legs_median %>% 
  mutate(date = as_date(date_time)) %>% 
  group_by(date) %>% 
  filter(alt > quantile(alt, 0.05), alt < quantile(alt, 0.95)) %>% 
  summarise(min_alt = min(alt), max_alt = max(alt), count = n()) %>% 
  mutate(change = max_alt-min_alt) %>% 
  arrange(desc(change))
```

Looks like 37.90 on 2019-08-30 is the largest real drop, although I know they drove on that day. Very difficult to tell


### Biggest VOC change in a day

```{r}
all_legs_median %>% 
  mutate(date = as_date(date_time)) %>% 
  group_by(date) %>% 
  filter(air_gas > quantile(air_gas, 0.05, na.rm = TRUE), air_gas < quantile(air_gas, 0.95,  na.rm = TRUE)) %>% 
  summarise(min_gas = min(air_gas), max_gas = max(air_gas), count = n()) %>% 
  mutate(change = max_gas-min_gas) %>% 
  arrange(desc(change))
```

Looks like the biggest "real" drop on a day with a reasonable amount of data is on 2019-11-21, with a drop of 1250505